\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2013-07-26 paper.tex
Tentative new title + abstract rewritten
The abstract is now more focused on AI

@@

\title{\LARGE \bf
Human-Robot Interaction: A Deliberative Architecture
}

@@

This paper addresses some key decisional issues that are necessary for a
cognitive robot which shares space and tasks with a human. We adopt a
constructive approach based on the identification and the effective
implementation of individual and collaborative skills. The system is
comprehensive since it aims at dealing with a complete set of abilities
articulated so that the robot controller is effectively able to conduct in a
flexible manner a collaborative task with a human partner. These abilities
include geometric reasoning and situation assessment based essentially on
perspective-taking and affordances, management and exploitation of each agent
(human and robot) knowledge in separate cognitive models, human-aware task
planning, and human and robot interleaved plan achievement.

This article presents our design choices, the articulations between the diverse
deliberative components of the robot, and the strengths and weaknesses of our
approach. We show that explicit knowledge management is not only a convenient
tool from the software engineering point of view, but also pushes for a
different, more \emph{semantic} way to address the decision-making issue in
human-robot interactions.

>>>>

\usepackage{booktabs}
%\usepackage{tabularx}

@@

\title{\LARGE \bf
Human-Robot Interaction: Tackling the AI Challenges
}

@@

Human-Robot interaction is an area filled with challenges for artifical
intelligence: dynamic, partially unknown environments that are not originally
designed for autonomous machines; a large variety of situations and objects to
deal with, with possibly complex semantics; physical interactions with humans
that requires fine, low-latency control, representation and management of
several mental models, good situation assessment skills...the list goes on.

This article shed light on some key decisional issues that are to be tackled
for a cognitive robot to share space and tasks with a human. We adopt a
constructive approach based on the identification and the effective
implementation of individual and collaborative skills. These cognitive
abilities cover geometric reasoning and situation assessment based essentially
on perspective-taking and affordances, management and exploitation of each
agent (human and robot) knowledge in separate cognitive models, natural
multi-modal communication, human-aware task planning, and human and robot
interleaved plan achievement.

We present our design choices, the articulations between the diverse
deliberative components of the robot, experimental results, and eventually
discuss the strengths and weaknesses of our approach. It appears that
\emph{explicit} knowledge management, both symbolic and geometric, proves to be
key as it pushes for a different, more \emph{semantic} way to address the
decision-making issue in human-robot interactions.
